Untitled

### 2025-03-14 script/r/rbci_data.Rmd
draft: desert control rds
cleanining

print(levels, n=40)
```

@@

#Adm setup

```{r}
cty_adm1 <- levels%>%
  filter(levels_nb>=1)%>%
  pull(country)

@@

```{r}
ggg_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

@@

    ggg_r5_adm1 <- rbind(ggg_r5_adm1, regions)

}

@@

saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1_bis.rds")
```

@@

```{r}
ggg_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r5_adm2 <- rbind(ggg_r5_adm2, regions)

}

@@

saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2_bis.rds")
```

@@

```{r}
ggg_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r5_adm3 <- rbind(ggg_r5_adm3, regions)

}

@@

saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3_bis.rds")
```

@@

```{r}
ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1_bis.rds")
ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2_bis.rds")
ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3_bis.rds")

@@

saveRDS(ggg_r5, file="data/data_rds/ggg_r5_bis.rds")
```

@@

```{r}
ggg_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r6_adm1 <- rbind(ggg_r6_adm1, regions)

}

@@

saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1_bis.rds")
```

@@

```{r}
ggg_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r6_adm2 <- rbind(ggg_r6_adm2, regions)

}

@@

saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2_bis.rds")

@@

```{r}
ggg_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r6_adm3 <- rbind(ggg_r6_adm3, regions)

}

@@

saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3_bis.rds")
```

@@

```{r}
ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1_bis.rds")
ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2_bis.rds")
ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3_bis.rds")

@@

saveRDS(ggg_r6, file="data/data_rds/ggg_r6_bis.rds")
```

@@

```{r}
ggg_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r7_adm1 <- rbind(ggg_r7_adm1, regions)

}

@@

saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1_bis.rds")
```

@@

```{r}
ggg_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r7_adm2 <- rbind(ggg_r7_adm2, regions)

}

@@

saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2_bis.rds")
```

@@

```{r}
ggg_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r7_adm3 <- rbind(ggg_r7_adm3, regions)

}

@@

saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3_bis.rds")
```

@@

```{r}
ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1_bis.rds")
ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2_bis.rds")
ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3_bis.rds")

@@

saveRDS(ggg_r7, file="data/data_rds/ggg_r7_bis.rds")
```

@@

```{r}
ggg_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r8_adm1 <- rbind(ggg_r8_adm1, regions)

}

@@

saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1_bis.rds")
```

@@

```{r}
ggg_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r8_adm2 <- rbind(ggg_r8_adm2, regions)

}

@@

saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2_bis.rds")
```

@@

```{r}
ggg_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    ggg_r8_adm3 <- rbind(ggg_r8_adm3, regions)

}

@@

saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3_bis.rds")
```

@@

```{r}
ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1_bis.rds")
ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2_bis.rds")
ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3_bis.rds")

@@

saveRDS(ggg_r8, file="data/data_rds/ggg_r8_bis.rds")
```

```{r}
ggg_r5 <- readRDS("data/data_rds/ggg_r5_bis.rds")
ggg_r6 <- readRDS("data/data_rds/ggg_r6_bis.rds")
ggg_r7 <- readRDS("data/data_rds/ggg_r7_bis.rds")
ggg_r8 <- readRDS("data/data_rds/ggg_r8_bis.rds")

@@

saveRDS(ggg_stack, file="data/data_rds/ggg_stack_bis.rds")
```

@@

```{r}
gg_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

@@

    gg_r5_adm1 <- rbind(gg_r5_adm1, regions)

}

@@

saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1_bis.rds")
```

@@

```{r}
gg_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r5_adm2 <- rbind(gg_r5_adm2, regions)

}

@@

saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2_bis.rds")
```

@@

```{r}
gg_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3_bis.rds")
```

@@

```{r}
gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1_bis.rds")
gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2_bis.rds")
gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3_bis.rds")

@@

saveRDS(gg_r5, file="data/data_rds/gg_r5_bis.rds")
```

@@

```{r}
gg_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r6_adm1 <- rbind(gg_r6_adm1, regions)

}

@@

saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1_bis.rds")
```

@@

```{r}
gg_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r6_adm2 <- rbind(gg_r6_adm2, regions)

}

@@

saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2_bis.rds")
```

@@

```{r}
gg_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r6_adm3 <- rbind(gg_r6_adm3, regions)

}

@@

saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3_bis.rds")
```

@@

```{r}
gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1_bis.rds")
gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2_bis.rds")
gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3_bis.rds")

@@

saveRDS(gg_r6, file="data/data_rds/gg_r6_bis.rds")

@@

```{r}
gg_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1_bis.rds")
```

@@

```{r}
gg_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r7_adm2 <- rbind(gg_r7_adm2, regions)

}

@@

saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2_bis.rds")
```

@@

```{r}
gg_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3_bis.rds")
```

@@

```{r}
gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1_bis.rds")
gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2_bis.rds")
gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3_bis.rds")

@@

saveRDS(gg_r7, file="data/data_rds/gg_r7_bis.rds")
```

@@

```{r}
gg_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1_bis.rds")
```

@@

```{r}
gg_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

    gg_r8_adm2 <- rbind(gg_r8_adm2, regions)

}

@@

saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2_bis.rds")
```

@@

```{r}
gg_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3_bis.rds")
```

@@

```{r}
gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1_bis.rds")
gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2_bis.rds")
gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3_bis.rds")

@@

saveRDS(gg_r8, file="data/data_rds/gg_r8_bis.rds")
```

```{r}
gg_r5 <- readRDS("data/data_rds/gg_r5_bis.rds")
gg_r6 <- readRDS("data/data_rds/gg_r6_bis.rds")
gg_r7 <- readRDS("data/data_rds/gg_r7_bis.rds")
gg_r8 <- readRDS("data/data_rds/gg_r8_bis.rds")

@@

saveRDS(gg_stack, file="data/data_rds/gg_stack_bis.rds")
```

##Merge internet

```{r}
gg_stack <- readRDS("data/data_rds/gg_stack_bis.rds")
ggg_stack <- readRDS("data/data_rds/ggg_stack_bis.rds")

int_stack_bis <- gg_stack %>%
  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

saveRDS(int_stack_bis, file="data/data_rds/int_stack_bis.rds")

int_stack_bis <- readRDS("data/data_rds/int_stack_bis.rds")

int_stack_bis%<>%
  mutate(pop_adm1= coalesce(pop_adm1.x, pop_adm1.y))%>%
  mutate(pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y))%>%
  mutate(pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y))

int_stack_bis%<>%
  select(-ends_with(".x"), -ends_with(".y"))

data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp.rds")

data_final_nlp_bis%<>%
  select(-c("gg_pop_adm1","gg_adm1","gg_adm1_pot","gg_pop_adm2","gg_adm2","gg_adm2_pot","gg_pop_adm3","gg_adm3","gg_adm3_pot","ggg_pop_adm1","ggg_adm1","ggg_adm1_pot","ggg_pop_adm2","ggg_adm2","ggg_adm2_pot","ggg_pop_adm3","ggg_adm3","ggg_adm3_pot","pop_adm1","pop_adm2","pop_adm3", "gg_region_pot", "ggg_region_pot", "cvg_region_pot", "cvg_region_pot_2"))

data_final_nlp_bis %<>%
  left_join(int_stack_bis, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

data_final_nlp_bis%<>%
mutate(gg_region_pot = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ gg_adm1_pot,
    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ gg_adm2_pot, 
    TRUE ~ NA_integer_
  ))%>%
mutate(ggg_region_pot = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ ggg_adm1_pot,
    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ ggg_adm2_pot, 
    TRUE ~ NA_integer_))%>%
  mutate(cvg_region_pot=ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))

data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp_bis.rds")

data_final_nlp_bis%<>%
mutate(pop_region = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ pop_adm1,
    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ pop_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(pop_region_log=log(pop_region+1))

data_final_nlp_bis2%<>%
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id())%>%
  ungroup()%>%
  mutate(adm1_time = case_when(
    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm1_time = as.integer(as.factor(adm1_time)))%>%
mutate(adm2_time = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm2_time = as.integer(as.factor(adm2_time)))

  data_final_nlp_bis2%<>%
  mutate(country_round=as.numeric(paste0(round,ccode)))%>%
  mutate(region_time = case_when(
    iso %in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name2_id * 10000 + round, 
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
  mutate(region_time = as.integer(as.factor(region_time)))

saveRDS(data_final_nlp_bis, file="data/data_rds/data_final_nlp_bis.rds")
write_dta(data_final_nlp_bis, "data/data_dta/data.dta")
```

@@

night_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

night_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

@@

```{r}
data_final_int <- readRDS("data/data_rds/data_final_nlp_bis.rds")
night_stack <- readRDS("data/data_rds/night_stack.rds")

@@

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

@@

```{r}
data_final_nlp_bis <- readRDS("data/data_rds/data_final_int_n_l.rds")

@@

data_keep <- subset(data_final_nlp_bis, select = c("id_unique", "latitude", "longitude")) %>%
  filter(!is.na(latitude) & !is.na(longitude))

@@

data_final_nlp_bis2%<>%
  select(-c( "area_0_km2", "area_1_km2", "area_2_km2", "area_3_km2"))

data_final_nlp_bis2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
  distinct(id_unique, .keep_all = TRUE)

saveRDS(data_final_nlp_bis2, file="data/data_rds/data_final_nlp_bis2.rds")
```

@@

```{r}
data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")

>>>>

print(levels, n=40)

cty_adm1 <- levels%>%
  filter(levels_nb>=1)%>%
  pull(country)

@@

@@

```{r}
ggg_r5_adm1 <- data.frame()

@@

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

@@

    ggg_r5_adm1 <- rbind(ggg_r5_adm1, regions)
}

@@

saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1.rds")
```

@@

```{r}
ggg_r5_adm2 <- data.frame()

@@

    ggg_r5_adm2 <- rbind(ggg_r5_adm2, regions)
}

@@

saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2.rds")
```

@@

```{r}
ggg_r5_adm3 <- data.frame()

@@

    ggg_r5_adm3 <- rbind(ggg_r5_adm3, regions)
}

@@

saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3.rds")
```

@@

```{r}
ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1.rds")
ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2.rds")
ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3.rds")

@@

saveRDS(ggg_r5, file="data/data_rds/ggg_r5.rds")
```

@@

```{r}
ggg_r6_adm1 <- data.frame()

@@

    ggg_r6_adm1 <- rbind(ggg_r6_adm1, regions)
}

@@

saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1.rds")
```

@@

```{r}
ggg_r6_adm2 <- data.frame()

@@

    ggg_r6_adm2 <- rbind(ggg_r6_adm2, regions)
}

@@

saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2.rds")
```

@@

```{r}
ggg_r6_adm3 <- data.frame()

@@

    ggg_r6_adm3 <- rbind(ggg_r6_adm3, regions)
}

@@

saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3.rds")
```

@@

```{r}
ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1.rds")
ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2.rds")
ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3.rds")

@@

saveRDS(ggg_r6, file="data/data_rds/ggg_r6.rds")
```

@@

```{r}
ggg_r7_adm1 <- data.frame()

@@

    ggg_r7_adm1 <- rbind(ggg_r7_adm1, regions)
}

@@

saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1.rds")
```

@@

```{r}
ggg_r7_adm2 <- data.frame()

@@

    ggg_r7_adm2 <- rbind(ggg_r7_adm2, regions)
}

@@

saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2.rds")
```

@@

```{r}
ggg_r7_adm3 <- data.frame()

@@

    ggg_r7_adm3 <- rbind(ggg_r7_adm3, regions)
}

@@

saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3.rds")
```

@@

```{r}
ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1.rds")
ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2.rds")
ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3.rds")

@@

saveRDS(ggg_r7, file="data/data_rds/ggg_r7.rds")
```

@@

```{r}
ggg_r8_adm1 <- data.frame()

@@

    ggg_r8_adm1 <- rbind(ggg_r8_adm1, regions)
}

@@

saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1.rds")
```

@@

```{r}
ggg_r8_adm2 <- data.frame()

@@

    ggg_r8_adm2 <- rbind(ggg_r8_adm2, regions)
}

@@

saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2.rds")
```

@@

```{r}
ggg_r8_adm3 <- data.frame()

@@

    ggg_r8_adm3 <- rbind(ggg_r8_adm3, regions)
}

@@

saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3.rds")
```

@@

```{r}
ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1.rds")
ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2.rds")
ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3.rds")

@@

saveRDS(ggg_r8, file="data/data_rds/ggg_r8.rds")
```

## Merge 3G

```{r}
ggg_r5 <- readRDS("data/data_rds/ggg_r5.rds")
ggg_r6 <- readRDS("data/data_rds/ggg_r6.rds")
ggg_r7 <- readRDS("data/data_rds/ggg_r7.rds")
ggg_r8 <- readRDS("data/data_rds/ggg_r8.rds")

@@

saveRDS(ggg_stack, file="data/data_rds/ggg_stack.rds")
```

@@

```{r}
gg_r5_adm1 <- data.frame()

@@

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

@@

    gg_r5_adm1 <- rbind(gg_r5_adm1, regions)
}

@@

saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1.rds")
```

@@

```{r}
gg_r5_adm2 <- data.frame()

@@

    gg_r5_adm2 <- rbind(gg_r5_adm2, regions)
}

@@

saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2.rds")
```

@@

```{r}
gg_r5_adm3 <- data.frame()

@@

saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3.rds")
```

@@

```{r}
gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1.rds")
gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2.rds")
gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3.rds")

@@

saveRDS(gg_r5, file="data/data_rds/gg_r5.rds")
```

@@

```{r}
gg_r6_adm1 <- data.frame()

@@

    gg_r6_adm1 <- rbind(gg_r6_adm1, regions)
}

@@

saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1.rds")
```

@@

```{r}
gg_r6_adm2 <- data.frame()

@@

    gg_r6_adm2 <- rbind(gg_r6_adm2, regions)
}

@@

saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2.rds")
```

@@

```{r}
gg_r6_adm3 <- data.frame()

@@

    gg_r6_adm3 <- rbind(gg_r6_adm3, regions)
}

@@

saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3.rds")
```

@@

```{r}
gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1.rds")
gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2.rds")
gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3.rds")

@@

saveRDS(gg_r6, file="data/data_rds/gg_r6.rds")
```

@@

```{r}
gg_r7_adm1 <- data.frame()

@@

saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1.rds")
```

@@

```{r}
gg_r7_adm2 <- data.frame()

@@

    gg_r7_adm2 <- rbind(gg_r7_adm2, regions)
}

@@

saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2.rds")
```

@@

```{r}
gg_r7_adm3 <- data.frame()

@@

saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3.rds")
```

@@

```{r}
gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1.rds")
gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2.rds")
gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3.rds")

@@

saveRDS(gg_r7, file="data/data_rds/gg_r7.rds")
```

@@

```{r}
gg_r8_adm1 <- data.frame()

@@

saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1.rds")
```

@@

```{r}
gg_r8_adm2 <- data.frame()

@@

    gg_r8_adm2 <- rbind(gg_r8_adm2, regions)
}

@@

saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2.rds")
```

@@

```{r}
gg_r8_adm3 <- data.frame()

@@

saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3.rds")
```

@@

```{r}
gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1.rds")
gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2.rds")
gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3.rds")

@@

saveRDS(gg_r8, file="data/data_rds/gg_r8.rds")
```

## Merge 2G

```{r}
gg_r5 <- readRDS("data/data_rds/gg_r5.rds")
gg_r6 <- readRDS("data/data_rds/gg_r6.rds")
gg_r7 <- readRDS("data/data_rds/gg_r7.rds")
gg_r8 <- readRDS("data/data_rds/gg_r8.rds")

@@

saveRDS(gg_stack, file="data/data_rds/gg_stack.rds")
```

# Merge Internet

```{r}
# -----------------------------------------------------------------------------
# MERGING AND PROCESSING REGIONAL INTERNET DATA
# -----------------------------------------------------------------------------

# -----------------------------------------------------------------------------
# 1. LOAD DATA
# -----------------------------------------------------------------------------
gg_stack <- readRDS("data/data_rds/gg_stack.rds")
ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")

# -----------------------------------------------------------------------------
# 2. MERGE DATASETS
# -----------------------------------------------------------------------------
# Merge gg_stack with ggg_stack by region identifiers and round
int_stack <- gg_stack %>%
  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

# Save intermediate merged internet dataset
saveRDS(int_stack, file = "data/data_rds/int_stack.rds")

# -----------------------------------------------------------------------------
# 3. CLEAN MERGED DATA
# -----------------------------------------------------------------------------
# Coalesce population variables from both datasets (take first non-NA value)
int_stack %<>%
  mutate(
    pop_adm1 = coalesce(pop_adm1.x, pop_adm1.y),
    pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y),
    pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y)
  )

# Remove duplicate columns ending with .x and .y
int_stack %<>%
  select(-ends_with(".x"), -ends_with(".y"))

# -----------------------------------------------------------------------------
# 4. MERGE WITH FINAL DATASET
# -----------------------------------------------------------------------------
# Load data_final dataset
data_final <- readRDS("data/data_rds/data_final.rds")

# Merge final dataset with internet stack
data_final %<>%
  left_join(int_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

# -----------------------------------------------------------------------------
# 5. REGION CLASSIFICATION
# -----------------------------------------------------------------------------
# Define country groups by administrative level
countries_adm1 <- c("GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

# -----------------------------------------------------------------------------
# 6. CREATE REGION POTENTIAL VARIABLES
# -----------------------------------------------------------------------------
# Generate region-specific variables based on country classification
data_final %<>%
  # Create gg region potential by admin level
  mutate(gg_region_pot = case_when(
    iso %in% countries_adm1 ~ gg_adm1_pot,
    iso %in% countries_adm2 ~ gg_adm2_pot,
    TRUE ~ NA_integer_
  )) %>%
  # Create ggg region potential by admin level
  mutate(ggg_region_pot = case_when(
    iso %in% countries_adm1 ~ ggg_adm1_pot,
    iso %in% countries_adm2 ~ ggg_adm2_pot,
    TRUE ~ NA_integer_
  )) %>%
  # Create combined coverage variable, prioritizing 3G data
  mutate(cvg_region_pot = ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))

# -----------------------------------------------------------------------------
# 7. POPULATION VARIABLES
# -----------------------------------------------------------------------------
# Create region-specific population density variables
data_final %<>%
  mutate(pop_region = case_when(
    iso %in% countries_adm1 ~ pop_adm1,
    iso %in% countries_adm2 ~ pop_adm2,
    TRUE ~ NA_integer_
  )) %>%
  mutate(pop_region_log = log(pop_region + 1))

# -----------------------------------------------------------------------------
# 8. CREATE REGION AND TIME IDENTIFIERS
# -----------------------------------------------------------------------------
# Generate unique IDs for regions and time periods
data_final %<>%
  # Create unique identifiers for administrative regions
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id()) %>%
  ungroup() %>%

  # Create time-region identifiers for ADM1
  mutate(adm1_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(adm1_time = as.integer(as.factor(adm1_time))) %>%

  # Create time-region identifiers for ADM2
  mutate(adm2_time = case_when(
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(adm2_time = as.integer(as.factor(adm2_time)))

# Create country-round and region-time identifiers
data_final %<>%
  mutate(country_round = as.numeric(paste0(round, ccode))) %>%
  # Create general region-time identifier based on administrative level
  mutate(region_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round,
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(region_time = as.integer(as.factor(region_time)))

# -----------------------------------------------------------------------------
# 9. SAVE FINAL DATASETS
# -----------------------------------------------------------------------------
# Save as R and Stata files
saveRDS(data_final, file = "data/data_rds/data_final.rds")
write_dta(data_final, "data/data_dta/data_final.dta")
```

@@

night_r5_adm1 <- data.frame()

@@

night_r5_adm2 <- data.frame()

@@

night_r5_adm3 <- data.frame()

@@

night_r6_adm1 <- data.frame()

@@

night_r6_adm2 <- data.frame()

@@

night_r6_adm3 <- data.frame()

@@

night_r7_adm1 <- data.frame()

@@

night_r7_adm2 <- data.frame()

@@

night_r7_adm3 <- data.frame()

@@

night_r8_adm1 <- data.frame()

@@

night_r8_adm2 <- data.frame()

@@

night_r8_adm3 <- data.frame()

@@

```{r}
data_final_int <- readRDS("data/data_rds/data_final_nlp.rds")
night_stack <- readRDS("data/data_rds/night_stack.rds")

@@

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

@@

```{r}
data_final_nlp <- readRDS("data/data_rds/data_final_int_n_l.rds")

@@

data_keep <- subset(data_final_nlp, select = c("id_unique", "latitude", "longitude")) %>%
  filter(!is.na(latitude) & !is.na(longitude))

@@

data_final_nlp2%<>%
  select(-c( "area_0_km2", "area_1_km2", "area_2_km2", "area_3_km2"))

data_final_nlp2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
  distinct(id_unique, .keep_all = TRUE)

saveRDS(data_final_nlp2, file="data/data_rds/data_final_nlp2.rds")
```

@@

```{r}
data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")
